An Algebraic Theory File Synchronization

### 2015-12-25 2015/algebra.tex
Fixed typos

Similarly to \cite{NREC} we can consider creating an algebra over command sequences
which will enable us to draw conclusions about the behaviours of the sequences
independently of filesystems.
This would provide a secondary model of (filesystem) commands above the model a filesystems
defined in this paper. The new model would no longer describe filesystems as such,
but use known relationships between sequences of commands as its starting point.

>>>>

Similarly to \cite{NREC} we can consider creating an algebra over command sequences
which will enable us to draw conclusions about the behaviors of the sequences
independently of filesystems.
This would provide a secondary model of (filesystem) commands above the model a filesystems
defined in this paper. The new model would no longer describe filesystems as such,
but use known relationships between sequences of commands as its starting point.

### 2015-12-25 2015/comparisons.tex
Reordering; improvements; new notation; improved figure
Fixed typos

We consider the reconciliation algorithm described here an improvement over
the one derved during our previous research (\cite{NREC})
as the previous algorithm not only fails to propagate all possible commands
wherever it is possible (that is, where it does not break the filesystem),
but the current algorithm is also simpler.
This is because the previous reconciliation algorithm excludes
commands from being propagated which must be preceded by a command that conflicts.

@@

It can be easily seen that not all conflicts detected based on the above definition
entails a conflict based on our system; that is, \cite{BP} describes a more
conservative policy.
For example, if $\nn=\parent(n)$ and $\FS(\nn)=\vald$ and $\FS(n)=\valf$, and
the two replicas are derived in the following way:
\begin{gather*}
\FS_A = \cfba{n} \cc \cdba{\nn} \FS \\
\FS_B = \cfba{n} \FS,
\end{gather*}
then $\nn$ is dirty in both replicas:
in $\FS_A$ it was modified, and in $\FS_B$ one of its descendants was modified.
Moreover, $\FS_A(\nn)\neq\FS_B(\nn)$ and $\FS_A(\nn)=\empt\not\in\setd$,
and therefore a conflict is detected at $\nn$.
Our reconciliation algorithm detects no conflicts;
instead, it propagates $\cdba{\nn}$ to $\FS_B$, which we think is as expected
and desired.

>>>>

We consider the reconciliation algorithm described here an improvement over
the one derived during our previous research (\cite{NREC})
as the previous algorithm not only fails to propagate all possible commands
wherever it is possible (that is, where it does not break the filesystem),
but the current algorithm is also simpler.
This is because the previous reconciliation algorithm excludes
commands from being propagated which must be preceded by a command that conflicts.

@@

It can be easily seen that not all conflicts detected based on the above definition
entails a conflict based on our system; that is, \cite{BP} describes a more
conservative policy.
For example, if $\nn=\parent(n)$ and $\FS(\nn)$ is a directory and $\FS(n)$ is a file, and
the two replicas are derived in the following way:
\begin{gather*}
\FS_A = \cfba{n} \cc \cdba{\nn} \aFS \\
\FS_B = \cfba{n} \aFS,
\end{gather*}
then $\nn$ is dirty in both replicas:
in $\FS_A$ it was modified, and in $\FS_B$ one of its descendants was modified.
Moreover, $\FS_A(\nn)\neq\FS_B(\nn)$ and $\FS_A(\nn)=\empt\not\in\setd$,
and therefore a conflict is detected at $\nn$.
Our reconciliation algorithm detects no conflicts;
instead, it propagates $\cdba{\nn}$ to $\FS_B$, which we think is as expected
and desired.
